\documentclass[article,11pt,letterpaper,fleqn]{article}
\usepackage{graphicx,color}
\usepackage{array}
\usepackage{threeparttable}
\usepackage[format=hang,font=normalsize,labelfont=bf]{caption}
\usepackage{colortbl}
\usepackage{multirow}
\usepackage{geometry}
\usepackage{subfigure}
\geometry{letterpaper,tmargin=1in,bmargin=1in,lmargin=1.25in,rmargin=1.25in}
\usepackage{hyperref}
\hypersetup{colorlinks,%
citecolor=red,%
filecolor=red,%
linkcolor=red,%
urlcolor=blue,%
pdftex}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{harvard}
\usepackage{tikz}
\usepackage{setspace}
\usepackage{float,graphicx,color}
\usepackage{appendix}
\usepackage{longtable}
\newtheorem*{thm}{Theorem}
\theoremstyle{definition}
\usepackage{lscape}
\numberwithin{equation}{section}
\newcommand{\cn}{\citeasnoun} % shortens command to cite as noun
\newcommand\ve{\varepsilon}


\title{Guide to Calibration of Household Income Processes in the OLG Dynamic Scoring Model}
\date{\today}



% make tables with smaller sized font 
\makeatletter
\def\table{\@ifnextchar[{\table@i}{\table@i[\fps@table]}}
\def\table@i[#1]{\@float{table}[#1]\footnotesize}
\makeatother



%\setlength{\topmargin}{-0.4in}
%\setlength{\topskip}{0.3in}    % between header and text
%\setlength{\textheight}{9.0in} % height of main text
%\setlength{\textwidth}{6in}    % width of text
%\setlength{\oddsidemargin}{39pt} %even side margin
%\setlength{\evensidemargin}{39pt} %odd side margin

\begin{document}
\bibliographystyle{aer}
\maketitle



\begin{abstract}
This will be the section in the dynamic scoring model handbook on calibrating parameters of household income processes.
\end{abstract}

\section{Panel Study of Income Dynamics}

To calibrate the parameters defining household income processes, we use the Panel Study of Income Dynamics (PSID).  We use the years 19XX-20XX.  From these, we draw the following variables...  All dollar values are deflated to 20XX dollars/ 

\subsection{Sample Selection}

We create a unique household identifier for combinations of head and spouse.  That is, we follow the household unit and not the individual.  We define the age of a household by the age of the head.

\section{Lifetime income}

In our model, lifetime income is endogenous.  We therefore seek to estimate the process for effective labor units for households over their lifecycle.  We define households by their lifetime income group.  Again, since income is endogenous, we create lifetime income groups by considering the expected, discounted expected value of lifetime labor endowments.\footnote{Note that the process for effective labor units is deterministic.  The uncertainty is over the exogenous probability of mortality.  The probability of mortality at each age, $s$, is the same across income groups, but can still affect the determination of different lifetime income groups since the probability of mortality varies by age, thus interacting with the lifecycle profile of labor endowments.} Our measure of lifetime income is the value of lifetime labor endowments, and not labor earnings.

Effective labor units from the model maps into hourly wage rates from the PSID data.

Our panel data do not allow us to observe the complete lifecycle of earnings for each household, thus we take a multi-step procedure to determining lifetime income for each household.  First, we impute hourly ages for years in each household's lifecycle that are not observed in the PSID.  To do this, we estimate the following equation, separately by household type (where household type is single male, single female, couple with male head, or couple with female head) :

\begin{equation}
\label{eqn:wage_step1}
ln(w_{i,t}) = \alpha_{i} + \beta_{1}age_{i,t} + \beta_{2}age_{i,t}^{2} + \beta_{3}*age_{i,t}^{3}+interactions with race and educaiton + \varepsilon_{i,t}
\end{equation}

When estimating this equation we only use non-zero observations of wages.

We then use the estimated coefficients and fixed effects from Equation \ref{eqn:wage_step1} to impute values for log wages for the year in each households economic life for which we do not have data.  This creates a balanced panel of log wages of households with heads from age 21 to 80.   

The imputed wage values are then used to calculate the net present value of lifetime labor endowments per adult for each household.  Specifically, we define lifetime income for household $i$ as: 

\begin{equation}
\label{eqn:LI}
LI_{i} = \sum_{t=21}^{80}  \left(\frac{1}{1+r}\right)^{t-21}w_{i,t}*4000)
\end{equation}

\noindent\noindent Note that households are all have the same time endowment in each year.  Thus the amount of the time endowment scales lifetime income up or down, but not change a households lifetime income relative to that of others.  This is not the case with the interest rate, $r$, which we fix a 4\%.  Changes in the interest rate would differentially impact the lifetime income calculation for different individuals because they may face different earnings profiles.  For example, a higher interest rate would lower lifetime income for those individuals whose wage profiles peaked later in their economic life by a larger amount than for individuals whose wage profiles peaked earlier.  

\section{Profiles by Lifetime Income}
With observations of lifetime income for each household, we next sort households and find the percentile of the lifetime income distribution that the household is in.  With these percentiles, we create our lifetime income groupings: $\lambda_{j}=[0.25, 0.25, 0.2, 0.1, 0.1, 0.09, 0.01]$. In this way, we separate these lifetime income groups.

To get an life-cyle profile of effective labor units for each group, we estimate the wage profile for each lifetime income group.  To do this, we estimate the following regression model separately for each lifetime income group using data on actual (not imputed) wages:

\begin{equation}
\label{eqn:wage_profile}
ln(w_{i,t})=\alpha +  \beta_{1}age_{i,t} + \beta_{2}age_{i,t}^{2} + \beta_{3}*age_{i,t}^{3}+ \varepsilon_{i,t}
\end{equation}


\bibliography{cons_calib_bib}

\end{document}